On the characteristic and diameter of planar integral point sets \footnote{ The work of the first author was partially supported by the Theoretical Physics and Mathematics Advancement Foundation “BASIS”. }

### 2024-10-09 char-4k-bound/char-4k-bound.tex
Switch to pregenerated references
[4k3] Last minor fixes

\usepackage[backend=biber,style=ajc2020unofficial]{biblatex}
\addbibresource{../common/notmy.bib}
\addbibresource{../common/my.bib}

%\usepackage{cite}

@@

\begin{definition}
	\label{def:IPS_semi_general}
	A planar IPS $M$ is said to be in \emph{semi-general position}
	if no three points of $M$ are collinear.
	Notation: $M\in\dot{\mathfrak{M}}$, and also $M\in\dot{\mathfrak{M}}_n$ for $n=\#M$.
\end{definition}

@@

\begin{definition}
	\label{def:IPS_general}
	A planar IPS $M$ is said to be in \emph{general position}
	if no three points of $M$ are collinear
	and no four points of $M$ are concircular.
	Notation: $M\in\overline{\mathfrak{M}}$, and also $M\in\overline{\mathfrak{M}}_n$ for $n=\#M$.
\end{definition}

@@

	The solution is
	\begin{gather}
		x = \frac{k^2 - n^2}{2 m} = \frac{a_i}{2m},
	\\
	%	y = \frac{\pm \sqrt{-(a^2 - b^2)^2 + m^2 (2 a^2 + 2 b^2  - m^2)} }{2m}.
		y = \pm\sqrt{k^2 - \left(\frac{m}{2}+x\right)^2} =
		\pm\sqrt{k^2 - \left(\frac{m}{2}+\frac{a_i}{2m}\right)^2} =
		\frac{\pm b_i \sqrt{q}}{2m},
	\end{gather}
	and the claim follows.
\end{proof}

@@

\begin{definition}
	A planar integral point set situated on two parallel straight lines
	is called a \emph{rails} set.
\end{definition}

@@

\printbibliography

>>>>

%\usepackage[backend=biber,style=ajc2020unofficial]{biblatex}
%\addbibresource{../common/notmy.bib}
%\addbibresource{../common/my.bib}

\usepackage{cite}

@@

\begin{definition}
	\label{def:IPS_semi_general}
	A planar IPS $M$ is said to be in \emph{semi-general position}
	if no three points of $M$ are collinear.
	Notation: $M\in\overline{\mathfrak{M}}$, and also $M\in\overline{\mathfrak{M}}_n$ for $n=\#M$.
\end{definition}

@@

\begin{definition}
	\label{def:IPS_general}
	A planar IPS $M$ is said to be in \emph{general position}
	if no three points of $M$ are collinear
	and no four points of $M$ are concircular.
	Notation: $M\in\dot{\mathfrak{M}}$, and also $M\in\dot{\mathfrak{M}}_n$ for $n=\#M$.
\end{definition}

@@

	The solution is
	\begin{gather}
		x = \frac{k^2 - n^2}{2 m} = \frac{a_i}{2m},
	\\
	%	y = \frac{\pm \sqrt{-(a^2 - b^2)^2 + m^2 (2 a^2 + 2 b^2  - m^2)} }{2m}.
		y = \pm\sqrt{k^2 - \left(\frac{m}{2}+x\right)^2} =
		\pm\sqrt{k^2 - \left(\frac{m}{2}+\frac{a_i}{2m}\right)^2} =
		\frac{\pm b_i \sqrt{p}}{2m},
	\end{gather}
	and the claim follows.
\end{proof}

@@

\begin{definition}
	A non-facher planar integral point set situated on two parallel straight lines
	is called a \emph{rails} set.
\end{definition}

@@

%\printbibliography

%\printbibitembibliography{}

\input{references.tex}
